Improving content discovery through combining linked data and data mining techniques

### 2016-05-06 report/report.tex
Trying to lay out abstract page

\begin{abstract}
\noindent MSc in Software Engineering and Internet Architecture 2016\\
\vspace{5mm}
\noindent Improving content discovery through combining linked data and data mining techniques\\
\vspace{5mm}
\noindent By Ross Fenning\\
\vspace{5mm}
\noindent Project Supervisor: Dr. D. Thakker\\
\vspace{5mm}
\vspace{5mm}
\noindent A comparative study of multiple approaches for extracting linked data
from web content published by the BBC for the purposes of applying
machine learning to cluster related content.

>>>>

\begin{abstract}
\vfill
\noindent MSc in Software Engineering and Internet Architecture 2016
\vfill
\noindent Improving content discovery through combining linked data and data mining techniques
\vfill
\noindent By Ross Fenning
\vfill
\noindent Project Supervisor: Dr. D. Thakker
\vfill
\noindent A comparative study of multiple approaches for extracting linked data
from web content published by the BBC for the purposes of applying
machine learning to cluster related content.
